\thispagestyle{empty}

\begin{center}

\rule{0mm}{3cm}

\textbf{\LARGE Coherence resonance in heterogeneous networks}

\vspace{4mm}

Chiara Mielau, Alexander Solovev, Vincent Stegmaier, Sven Zimmermann

\vspace{2mm}

Betreuer: Leonhard Schülen

\vspace{4cm}

\begin{minipage}[c]{0.7\textwidth}
	\begin{center}
		\textbf{\large Task}
	\end{center}
	The counter-intuitive effect of coherence resonance describes a non-monotonic behavior of the
	regularity of noise-induced oscillations in the excitable regime, leading to an optimum response
	in terms of regularity of the excited oscillations for an intermediate noise strength \cite{Pikovsky1997}. Coherence
	resonance has been investigated in complex networks with local, nonlocal and global topologies as
	well as in random and small-world networks \cite{Masoliver2017}. The phenomenon of coherence resonance has been
	also recently studied in a two-layer multiplex network \cite{Semenova2018}. In \cite{Masoliver2017} and \cite{Semenova2018} the network elements are
	all assumed to be identical. In real-world systems, however, the elements are often non-identical.
	The goal of this project is to investigate the impact of heterogeneity on coherence resonance.
	
	\begin{itemize}
		\item Perform a literature search about this topic. Has coherence resonance been previously investigated in networks with heterogeneous elements?
		\item Reproduce the results (without delays) obtained in \cite{Masoliver2017}. In particular, reproduce Fig. 2.
		\item Consider the case of inhomogeneous FitzHugh-Nagumo neurons in excitable regime. For example, $a_i$ is normally distributed around the value 1.1. 
			Make sure that that $a_i > 1 \forall i$ as this is the bifurcation point. Perform a simulation for $\sigma = 0.1$ and $D = 0.001$. What are the effects of the inhomogeneities?
		\item  Try to get a similar curve as in Fig. 2, now for the inhomogeneities. Is the picture similar or does it deviate significantly?
			 If so, is the effect dependent on the noise intensity/the coupling strength?
	\end{itemize}
\end{minipage}

\end{center}

\newpage

\tableofcontents
\thispagestyle{empty}

\setcounter{page}{0}